Imputation of Incomplete Multilevel Data with \pkg{mice}

### 2021-12-21 Manuscript/Manuscript.tex
Add parameters estimates popularity data
Valentijn's comments and suggestions.

\author{
Hanne Oberman\\Utrecht University \And Johanna Munoz Avila\\University
Medical Center Utrecht \AND Valentijn de Jong\\University Medical
Center Utrecht \And Gerko Vink\\Utrecht University \AND Thomas
Debray\\University Medical Center Utrecht
}
\title{Imputation of Incomplete Multilevel Data with \pkg{mice}}

\Plainauthor{Hanne Oberman, Johanna Munoz Avila, Valentijn de
Jong, Gerko Vink, Thomas Debray}
\Plaintitle{Imputation of Incomplete Multilevel Data with mice}
\Shorttitle{Multilevel \pkg{mice}}

\Abstract{
Multilevel data is not spared the ubiquitous problem of missing
information. This is a tutorial paper on imputing incomplete multilevel
data with \pkg{mice}. Including methods for ignorable and non-ignorable
missingness. Footnotes in the current version show work in
progress/under construction. The last section is not part of the
manuscript, but purely for reminders.
}

@@

\usepackage{graphicx}
\usepackage{mathtools}

@@

Research into any field with a hierarchical or clustered nature of
observations may yield multilevel data. In the typical case, individuals
are nested within groups, but there are many different types of
multilevel data. In the medical field, clustering occurs at e.g., the
hospital or center level in registry data, or at the study-level in
meta-analyses (IPDMA\footnote{remove or write in full?}). In the social
sciences and official statistics we can find clustering e.g.~at the
country-level, or as imposed by a multi-stage sampling design. For the
sake of legibility, we will refer to the grouping variable as `cluster',
and the grouped variable as `(sample) unit' throughout this
paper.\footnote{Alternatives to unit: participant/response/record.} And,
for reasons of brevity, we only discuss clustering between units, not
within units (e.g., timeseries or longitudinal data).\footnote{Also, add
  that we'll only discuss two levels, not more?}

Analyzing multilevel data requires special care, compared to `regular',
single level data. For instance, there may be cross-level interactions
between unit-level variables and cluster-level variables. The cluster to
which a unit belongs may influence the unit-level observations, and vice
versa for the the units that make up the cluster \citep{hox17}. These
relations can and should be taken into account when developing analysis
models for multilevel data.\footnote{Explain ICC here? The percentage of
  variance attributed to the cluster-level is expressed by the
  intra-class coefficient (ICC). The ICC can also be interpreted as the
  expected correlation between two randomly sampled units in same
  cluster. So if the ICC is high, a lot of variability in a variable is
  due to the clustering, which should be modeled accordingly.}
Multilevel models typically include separate intercepts for each
cluster, which relieves one restriction imposed by single-level models:
equal group means across clusters. Additionally, there may be random
predictor effects and/or random error terms (residual error variances),
see e.g. \citet{hox17} and \citet{jong21}.\footnote{Add that
  heterogeneity refers to variability within clusters.} There are many
names for models that take clustering into account. Some popular
examples are `multilevel models', `hierarchical models', `mixed effect
models' and `random effect models'.

@@

Multilevel data is not spared the ubiquitous problem of missing
information. Just as in single level data, missingness may occur at the
unit level. But with multiple levels of data comes the potential for
missingness at multiple levels. Missingness in multilevel data can be
categorized into two general patterns: systematical missingness and
sporadic missingness, see \citet{resc13}. In figure 1, we show a dataset
with units in the rows and variables in the columns, there are 5 units
nested within 3 clusters, and 3 variables of interest. Variable
\texttt{X1} is completely observed. Variable \texttt{X2} is
systematically missing, \texttt{X3} is sporadically missing.\footnote{Explain
  why.} Systematic missingness can be further subdivided into unobserved
constants (i.e., the same value within clusters) and non-measured random
variables (which may differ per unit within clusters). In Figure 1, the
former implies that the unobserved values for units 3 and 4 on variable
\texttt{X2} would be equal. With the latter, the values may differ.
Depending on the missing data pattern\footnote{add missing data
  mechanisms here?}, there are more or less optimal way of accommodating
the missingness.

\[
\begin{matrix} 
                          &X1     & X2          & X3            \\
   \hline
   \mathrm{cluster 1}\{   &x_{11} &x_{12}       &\mathtt{NA}    \\
                          &x_{21} &x_{22}       &x_{32}         \\
   \mathrm{cluster 2}\{   &x_{31} &\mathtt{NA}  &x_{33}         \\
                          &x_{41} &\mathtt{NA}  &\mathtt{NA}    \\
   \mathrm{cluster 3}\{   &x_{51} &x_{52}       &x_{53}         \\
\end{matrix} 
\]

Ignoring missing data in research endeavors is almost never a good idea.
Complete case analysis (i.e., excluding all units with one or more
missing entries) can introduce bias in statistical inference and lowers
statistical power. Instead, the missingness should be accommodated
\emph{before} or \emph{within} the analysis of scientific interest.
Especially the former is very generic and popular. Imputing (i.e.,
filling in) the missing values splits the missing data problem from the
scientific problem. The \proglang{R} package \pkg{mice} has become the
de-facto standard for imputation by chained equations, which solves the
missingness one variable at a time, iteratively. \pkg{mice} is known to
yield valid inferences under many different missing data circumstances
\citep{buur18}. In this paper, we'll discuss how to use \pkg{mice} in
the context of multilevel data, under varying missing data
mechanisms.\footnote{Discuss missingness mechanisms before this point,
  add references \citet{yuce08} and \citet{hox15}.}

@@

This papers serves as a tutorial for imputing incomplete multilevel data
with \pkg{mice}. We provide practical guidelines and code snippets for
different missing data situations. For reasons of brevity, we focus on
imputation by chained equations\footnote{add that JOMO is available in
  \pkg{mice} as well?}. Other useful packages for incomplete multilevel
data include \pkg{mitml}, \pkg{miceadds}, and \pkg{mdmb}.\footnote{Rephrase:
  Some level of knowledge on multilevel models is assumed. We're
  providing an overview of implementations. It's up-to the reader to
  decide which multilevel strategy suits their data. So we won't go into
  detail for the different methods (and equations). Refer to
  \citet{meng94}, \citet{audi18}, and \citet{grun18}. This paper is just
  a software tutorial. We'll keep it practical.}

@@

For each case study we focus on a different aspect to illustrate how to
impute incomplete multilevel data. In the \texttt{mice::popmis} data, we
show the advantages of including the multilevel structure of the data
into the imputation model. In the \texttt{metamisc::impact} data we'll
show how to induce missingness and solve it in real-world data. In the
\texttt{GJRM::hiv} we provide novel methodology\footnote{not really, the
  methods exist already, but how to show that this is something new and
  exciting?} for imputing MNAR missingness according to the Heckman
model. For all case studies we discuss the nature of the incomplete
data, the imputation model(s), and evaluation of the imputed data.

\hypertarget{case-study-i-popularity}{%
\section{Case Study I: Popularity}\label{case-study-i-popularity}}

\texttt{popNCR} is a simulated dataset with pupils clustered in classes,
where the number of units \(n = 2000\), and the number of clusters
\(N = 100\), on 7 variables:

@@

The popularity data is created such that there are strong relations
between the incomplete variables and the clustering variable
\texttt{class}. We can express this using the intra-class correlation
(ICC). For \texttt{popular} the ICC is 0.33. For \texttt{popteach} it is
0.34. It would thus be wise to use multilevel modeling.

The missingness in this dataset is induced conform MAR and MNAR
mechanisms. The missing data pattern, Figure \ref{fig:pop_pat}, shows
that just one variable is incomplete \textbf{{[}the next part is not yet
updated to reflect this{]}}.

@@

In Figure \ref{fig:pop_dist} we see that the distribution for the
missing \texttt{popular} is further to the right than the distribution
for observed \texttt{popular}. This would indicate a right-tailed MAR
missingness. In fact, this is exactly what happens, because the
missingness in these data was created manually. Now, we've made it
observable by examining the relations between the missingness in popular
and the observed data in \texttt{popteach}. There is also a dependency
between the missingness in teacher popularity and pupil popularity. The
relation seems to be right-tailed as well.

@@

\caption[Conditional distributions in the popularity data]{Conditional distributions in the popularity data}\label{fig:pop_dist}
\end{figure}
\end{CodeChunk}

@@

The first imputation model that we'll use is likely to be invalid. In
this model, we ignore the multilevel structure of the data, despite the
high ICCs. This is purely to illustrate the effects of ignoring the
clustering in our imputation effort.

We'll use predictive mean matching to impute the continuous variables
and logistic regression to impute the binary variable \texttt{sex}. We
do not use the observation identifier \texttt{pupil} or cluster
identifier \texttt{class} as predictors to impute other variables.

\begin{CodeChunk}
\begin{CodeInput}
R> # dry run to get imputation parameters
R> ini <- mice(pop, maxit = 0)
R> 
R> # extract predictor matrix and adjust
R> pred <- ini$pred
R> pred[, c("class", "pupil")] <- 0
R> 
R> # impute the data, ignoring the cluster structure
R> imp_ignored <- mice(pop, maxit = 1, pred = pred, print = FALSE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeOutput}
      vars incomplete   ignored
1  popular  0.3280070 0.3338626
2 popteach  0.3414766 0.3414766
3     texp  1.0000000 1.0000000
\end{CodeOutput}
\end{CodeChunk}

@@

We can also observe that the teacher experience increases slightly after
imputation. This is due to the MNAR missingness in \texttt{texp}. Higher
values for \texttt{texp} have a larger probability to be missing. This
may not a problem, however, if at least one pupil in each class has
teacher experience recorded, we can deductively impute the correct
(i.e.~true) value for every pupil in the class.

@@

We'll now use \texttt{class} as a predictor to impute all other
variables. This is still not recommended practice, since it only works
under certain circumstances and results may be biased. But at least, it
includes some multilevel aspect. Colloquially, this is `multilevel
imputation for dummies'.

\begin{CodeChunk}
\begin{CodeInput}
R> # adjust the predictor matrix
R> pred <- ini$pred 
R> pred[, "pupil"] <- 0
R> 
R> # impute the data, cluster as predictor
R> imp_predictor <- mice(pop, maxit = 1, pred = pred, print = FALSE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeOutput}
      vars incomplete   ignored predictor
1  popular  0.3280070 0.3338626 0.3871020
2 popteach  0.3414766 0.3414766 0.3414766
3     texp  1.0000000 1.0000000 1.0000000
\end{CodeOutput}
\end{CodeChunk}

@@

\begin{CodeChunk}
\begin{CodeInput}
R> pred <- ini$pred
R> pred["popular", ] <- c(0, -2, 2, 2, 2, 0, 2) 
R> #-2 for the cluster variable, 2 for random effects
R> meth <- ini$meth
R> meth <- c("", "", "", "", "", "2l.norm", "")
R> imp_norm_2l <-
+   mice(
+     pop %>% mutate(class = as.integer(class)),
+     pred = pred,
+     meth = meth,
+     maxit = 1,
+     print = FALSE
+   )
\end{CodeInput}
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeInput}
R> # plot(imp_norm)
R> plot_box(imp_norm_2l, x = "popular", strip = TRUE)
\end{CodeInput}

\begin{center}\includegraphics{Manuscript_files/figure-latex/pop_norm_eval-1} \end{center}

\begin{CodeInput}
R> ICCs <- ICCs %>% mutate(
+            norm = c(icc(popular ~ as.factor(class), complete(imp_norm_2l)), 
+                     icc(popteach ~ as.factor(class), complete(imp_norm_2l)), 
+                     icc(texp ~ as.factor(class), complete(imp_norm_2l)))
+            )
R> ICCs
\end{CodeInput}
\begin{CodeOutput}
      vars incomplete   ignored predictor      norm
1  popular  0.3280070 0.3338626 0.3871020 0.3612830
2 popteach  0.3414766 0.3414766 0.3414766 0.3414766
3     texp  1.0000000 1.0000000 1.0000000 1.0000000
\end{CodeOutput}
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeInput}
R> pred["popular", ] <- c(0, -2, 2, 2, 1, 0, 2)
R> meth <- c("", "", "", "", "", "2l.pan", "")
R> imp_pan_2l <-
+   mice(
+     pop %>% mutate(class = as.integer(class)),
+     pred = pred,
+     meth = meth,
+     maxit = 1,
+     print = FALSE
+   )
\end{CodeInput}
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeInput}
R> # plot(imp_pan)
R> plot_box(imp_pan_2l, x = "popular", strip = TRUE)
\end{CodeInput}

\begin{center}\includegraphics{Manuscript_files/figure-latex/pop_pan_eval-1} \end{center}

\begin{CodeInput}
R> ICCs <- ICCs %>% mutate(
+            pan = c(icc(popular ~ as.factor(class), complete(imp_pan_2l)), 
+                     icc(popteach ~ as.factor(class), complete(imp_pan_2l)), 
+                     icc(texp ~ as.factor(class), complete(imp_pan_2l)))
+            )
R> ICCs
\end{CodeInput}
\begin{CodeOutput}
      vars incomplete   ignored predictor      norm       pan
1  popular  0.3280070 0.3338626 0.3871020 0.3612830 0.3745108
2 popteach  0.3414766 0.3414766 0.3414766 0.3414766 0.3414766
3     texp  1.0000000 1.0000000 1.0000000 1.0000000 1.0000000
\end{CodeOutput}
\end{CodeChunk}

\hypertarget{case-study-ii-impact}{%
\section{Case study II: IMPACT}\label{case-study-ii-impact}}

\texttt{impact} is traumatic brain injury data with patients,
\(n = 11022\), clustered in studies, \(N = 15\). With the following 11
variables:

@@

\hypertarget{case-study-iii-hiv}{%
\section{Case study III: HIV}\label{case-study-iii-hiv}}

Toy example from
\href{https://github.com/johamunoz/Heckman-IPDMA/blob/main/Toy_example.R}{Heckman
Github repo}.

@@

\begin{itemize}
\item
  Adding some kind of help function to mice that suggests a suitable
  predictor matrix to the user, given a certain analysis model.
\item
  Adding a \texttt{multilevel\_ampute()} wrapper function in mice.
\item
  Exporting \texttt{mids} objects to other packages like \texttt{lme4}
  or \texttt{coxme}?
\item
  Adding a ICC=0 dataset to show that even if there is no clustering it
  doesn't hurt.
\end{itemize}

>>>>

\author{
Hanne Oberman\\Utrecht University \And Johanna Munoz Avila\\University
Medical Center Utrecht \AND Valentijn M.T. de Jong\\University
Medical Center Utrecht, EMA \And Gerko Vink\\Utrecht University
\AND Thomas P.A. Debray\\University Medical Center Utrecht
}
\title{Imputation of Incomplete Multilevel Data with \pkg{mice}}

\Plainauthor{Hanne Oberman, Johanna Munoz Avila, Valentijn M.T. de
Jong, Gerko Vink, Thomas P.A. Debray}
\Plaintitle{Imputation of Incomplete Multilevel Data with mice}
\Shorttitle{\pkg{mice}: Multilevel}

\Abstract{
Tutorial paper on imputing incomplete multilevel data with \pkg{mice}.
Including methods for ignorable and non-ignorable missingness.
}

@@

@@

We talk of multilevel data when there is some kind of hierarchy or
clustering in a data set. In the typical case, individuals are nested
within groups, but there are many different types of multilevel data. In
the medical field, clustering occurs at e.g., the hospitals/center level
in registry data, or at the study-level in individual participant data
meta-analyses (IPDMA). In the social sciences and official statistics we
can find clustering e.g.~at the country-level, or as imposed by the
sampling design. In this paper, we will refer to the grouping variable
as `cluster', and the grouped variable as `(sample) unit'.\footnote{Add
  that we'll only discuss two levels?} For reasons of brevity, we only
discuss clustering between units, not within units (such as in
timeseries or longitudinal data).

Analyzing multilevel data requires special care, compared to `regular',
single level data. The cluster to which a unit belongs may influence the
unit-level observations, and since clusters are made up of units,
clusters depend on units as well \citep{hox17}. These relations can and
should be taken into account when developing analysis models for
multilevel data.\footnote{Explain ICC here? The percentage of variance
  attributed to the cluster-level is expressed by the intra-class
  coefficient (ICC). The ICC can also be interpreted as the expected
  correlation between two randomly sampled units in same cluster. So if
  the ICC is high, a lot of variability in a variable is due to the
  clustering, which should be modeled accordingly.} Multilevel models
typically include separate intercepts for each cluster, which relieves
one restriction imposed by single-level models: equal group means across
clusters. Additionally, there may be random predictor effects and/or
random error terms (residual error variances), see e.g. \citet{hox17}
and \citet{jong21}.\footnote{Add that heterogeneity refers to
  variability within clusters. VDJ: heterogeneity can refer to
  variability of sample units, i.e.~variance. It can also refer to
  variability across data sets: variability in measurement instruments,
  definitions, but also to variability of treatment/predictor effects
  across data sets} There are many names for models that take clustering
into account. Some popular examples are `multilevel models',
`hierarchical models', `mixed effect models' and `random effect models'.

@@

Multilevel data is not spared the ubiquitous problem of missing
information. Just as in single level data, missingness may occur at the
unit level. But with multiple levels of data comes the potential for
missingness at multiple levels. Missingness in multilevel data can be
categorized into two general patterns: systematical missingness and
sporadic missingness, see \citet{resc13}. In figure 1, we show a data
set with units in the rows and variables in the columns, there are 5
units nested within 2 clusters, and 3 variables of interest. Variable
\texttt{X1} is completely observed. Variable \texttt{X2} is
systematically missing in cluster 2, \texttt{X3} is sporadically missing
in both clusters.\footnote{Explain why.} Systematic missingness can be
further subdivided into unobserved constants (same value per cluster)
and non-measured random variables (which may differ per unit within
clusters). In Figure 1, the former implies that the unobserved values
for units 4 and 5 on variable \texttt{X2} would be equal. With the
latter, the values may differ. The optimal way of accomodating the
missingness may depend on the missing data pattern.

Ignoring missing data in research endeavors is almost never a good idea.
Complete case analysis (i.e., excluding all units with one or more
missing entries) can introduce bias in statistical inference and lowers
statistical power. Instead, the missingness should be accommodated
\emph{before} or \emph{within} the analysis of scientific interest.
\footnote{Can you give an example of each? With within do you mean
  integrating missing data out, or automatic imputation in a Bayesian
  MCMC analysis?. One might also think that with before you mean
  contacting the sample units to obtain the true values, which would
  then conflict with the remainder of the paragraph.}Especially the
former is very generic and popular. Imputing (i.e., filling in) the
missing values splits the missing data problem from the scientific
problem. The \proglang{R} package \pkg{mice} has become the de-facto
standard for imputation by chained equations, which solves the
missingness one variable at a time, iteratively. \pkg{mice} is known to
yield valid inferences under many different missing data circumstances
\citep{buur18}. In this paper, we'll discuss how to use \pkg{mice} in
the context of multilevel data, under varying missing data
mechanisms.\footnote{Discuss missingness mechanisms before this point,
  add references \citet{yuce08} and \citet{hox15}.}

@@

This papers serves as a tutorial for imputing incomplete multilevel data
with \pkg{mice}. We provide practical guidelines and code snippets for
different missing data situations. For reasons of brevity, we focus on
imputation by chained equations, although JOMO is available in
\pkg{mice} as well. Other useful packages for incomplete multilevel data
include: \pkg{mitml}, \pkg{miceadds}, \pkg{mdmb}.\footnote{Rephrase:
  Some level of knowledge on multilevel models is assumed. We're
  providing an overview of implementations. It's up-to the reader to
  decide which multilevel strategy suits their data. So we won't go into
  detail for the different methods (and equations). Refer to
  \citet{meng94}, an Audigier paper, and a paper by Grund on
  congeniality and random slopes. This paper is just a software
  tutorial. We'll keep it practical.}

@@

For each case study we focus on a different aspect to illustrate how to
impute incomplete multilevel data.

\hypertarget{workflows}{%
\section{Workflows}\label{workflows}}

We introduce three case studies to illustrate the workflow. In the
\texttt{mice::popmis} data, we show the advantages of including the
multilevel structure of the data into the imputation model. In the
\texttt{metamisc::impact} data we'll show how to induce missingness and
solve it in real-world data. In the \texttt{GJRM::hiv} we provide novel
methodology\footnote{not really, the methods exist already, but how to
  show that this is something new and exciting?} for imputing MNAR
missingness according to the Heckman model.

For each case study we'll look at least at: 1) the incomplete data; 2)
the imputation model; 3) the imputed data; and 4) how to obtain pooled
estimates for the analysis of scientific interest.

\hypertarget{case-study-i-popularity}{%
\subsection{Case Study I: Popularity}\label{case-study-i-popularity}}

\texttt{popNCR} is a simulated data set with pupils clustered in
classes, \(n_{\text{participants}} = 2000\),
\(n_{\text{clusters}} = 100\), on 7 variables:

@@

The popularity data is created such that there are strong relations
between the incomplete variables and the clustering variable
\texttt{class}. We can express this using the intra-class correlation
(ICC). For \texttt{popular} the ICC is 0.33. For \texttt{popteach} it is
0.31. It would thus be wise to use multilevel modeling.

The missingness in this data set is induced conform MAR and MNAR
mechanisms. The missing data pattern, Figure \ref{fig:pop_pat}, shows
the systematic nature of the missingness.

@@

In Figure \ref{fig:pop_dist} we see that the distribution for the
missing \texttt{popular} is further to the right than the distribution
for observed \texttt{popular}. \footnote{Isn't it the other way around?.}
This would indicate a right-tailed MAR missingness. In fact, we know
that this is exactly what happened, because the missingness in these
data was created manually. Now, we've made it observable by examining
the relations between the missingness in popular and the observed data
in \texttt{popteach}. There is also a dependency between the missingness
in teacher popularity and pupil popularity. The relation seems to be
right-tailed as well.

@@

\caption[Conditional distributions in the popularity data]{Conditional distributions in the popularity data}\label{fig:pop_dist-1}
\end{figure}
\begin{figure}

{\centering \includegraphics{Manuscript_files/figure-latex/pop_dist-2}

\caption[Conditional distributions in the popularity data]{Conditional distributions in the popularity data}\label{fig:pop_dist-2}
\end{figure}
\end{CodeChunk}

@@

In the first imputation model that we'll use, we ignore the multilevel
structure of the data despite the high ICCs. This model is likely to be
invalid. We apply it purely to illustrate the effects of ignoring the
clustering in our imputation effort.

We'll use predictive mean matching to impute the continuous variables
and logistic regression to impute the binary variable \texttt{sex}. We
do not use the observation identifier \texttt{pupil} or cluster
identifier \texttt{class} as predictors to impute other
variables.\footnote{Explain why.}

\begin{CodeChunk}
\begin{CodeInput}
R> # dry run to get imputation parameters
R> ini <- mice(pop, maxit = 0)
R> 
R> # extract predictor matrix and adjust
R> pred <- ini$pred
R> pred[, c("class", "pupil")] <- 0
R> 
R> # impute the data, ignoring the cluster structure
R> imp_ignored <- mice(pop, maxit = 10, pred = pred, print = FALSE)
\end{CodeInput}
\end{CodeChunk}

@@

\begin{CodeOutput}
      vars incomplete   ignored
1  popular  0.3280070 0.2867315
2 popteach  0.3138658 0.2541582
3     texp  1.0000000 0.4329458
\end{CodeOutput}
\end{CodeChunk}

@@

We can also observe that the teacher experience increases slightly after
imputation. This is due to the MNAR missingness in \texttt{texp}.
\footnote{Mention somewhere around here that texp an unobserved
  constant, which you mentioned in the introduction?} Higher values for
\texttt{texp} have a larger probability to be missing. This may not be a
problem, however, if at least one pupil in each class has teacher
experience recorded, we can deductively impute the correct (i.e.~true)
value for every pupil in the class. \footnote{But is it reallly MNAR if
  we can restore it by simply using the observed data?}

@@

We'll now use \texttt{class} as a predictor to impute all other
variables. This is not recommended practice, since it only works under
certain circumstances \footnote{Explain why. Because it does not borrow
  information across classes? or because of this specific example where
  texp is given by class?} and results may be biased. \footnote{Why
  would it be biased? Typically fixed effects models (i.e.~estimated per
  cluster) are unbiased, are you saying this is different for imputation
  models?} But at least, it includes some multilevel aspect.
Colloquially, this is `multilevel imputation for dummies'.

@@

\begin{CodeOutput}
      vars incomplete   ignored predictor
1  popular  0.3280070 0.2867315 0.3825608
2 popteach  0.3138658 0.2541582 0.2541437
3     texp  1.0000000 0.4329458 1.0000000
\end{CodeOutput}
\end{CodeChunk}

@@

\hypertarget{case-study-ii-impact}{%
\subsection{Case study II: IMPACT}\label{case-study-ii-impact}}

\texttt{impact} is traumatic brain injury data with patients clustered
in studies, \(n_{\text{participants}} = 11022\) and
\(n_{\text{clusters}} = 15\), on the following 11 variables:

@@

\hypertarget{pooling}{%
\subsection{Pooling}\label{pooling}}

\begin{itemize}
\item
  Analysis of scientific interest.
\item
  Pooling using \texttt{mitml}.
\item
  Pooling `regular' parameters vs more `exotic' parameters (SE of
  residual errors, or autocorrelation)
\end{itemize}

@@

\begin{itemize}
\item
  Adding some kind of help function to mice that suggests a suitable
  predictor matrix to the user, given a certain analysis model.
\item
  Adding a \texttt{multilevel\_ampute()} wrapper function in mice.
\item
  Exporting \texttt{mids} objects to other packages like \texttt{lme4}
  or \texttt{coxme}?
\end{itemize}
